Tests for Measurement Invariance When Subgroups Are Unknown

### 2012-07-07 imps2012/invariance.tex
added ordinal test statistics
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@149 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

\frame{
  \frametitle{Tests along Ordinal Variables}
  \begin{itemize}
    \item Instead of aggregating over all $i = 1, \dots, n$, aggregate
      only over $i_\ell = \lfloor n \cdot t_\ell\rfloor$ for the cumulative proportions
      $t_\ell$ ($\ell = 1, \dots, m$).
    \item Tests: Obtain ordinal versions of the max LM test and (weighted) double maximum test.
      Additionally use LM-type test that does not exploit ordering.
    \begin{eqnarray*}
      \mathit{WDM}_o & = & \max_{i \in \{i_1, \dots, i_m \}} ~ \left\{ \frac{i}{n} \left( 1 - \frac{i}{n} \right) \right\}^{-1}      
                             \max_{j = 1, \dots, k} | {\bm B}(\hat {\bm \theta})_{ij} |,\\
      \max \mathit{LM}_o & = & \max_{i \in \{i_1, \dots, i_m \}} ~
                             \left\{ \frac{i}{n} \left( 1 - \frac{i}{n} \right) \right\}^{-1}
                             \sum_{j = 1, \dots, k} {\bm B}(\hat {\bm \theta})_{ij}^2,\\
      \mathit{LM}_\mathit{uo} & = & \sum_{\ell = 1, \dots, m+1} \sum_{j = 1, \dots, k}
        \left( {\bm B}(\hat {\bm \theta})_{i_\ell j} - {\bm B}(\hat {\bm \theta})_{i_{\ell - 1}j} \right)^2.
    \end{eqnarray*}
  \end{itemize}}
